\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2024-04-17 paper.tex
Update

% NEEDS REWRITE
\begin{abstract}
As a result of recombination, adjacent nucleotides can have
different paths of genetic inheritance and therefore
the genealogical trees for
% surely saying nucleotides and "sample of sequences" is concrete enough
% here? This paper isn't for a general audience, let's just say what
% we're talking about in direct language understandable by population
% geneticists.
a sample of DNA sequences vary along the genome.
The structure capturing the details of these intricately interwoven paths of
inheritance is referred to as an ancestral recombination graph (ARG).
% New developments have made it possible to infer ARGs at scale,
% enabling many new applications in population and statistical genetics.
% This rapid progress has led to a diversity of ARG definitions and representations.
Classical formalisms have focused on mapping 
coalescence and recombination events to the nodes in an ARG.
We show that this approach is out of step with modern developments,
which do not represent genetic inheritance in terms of these events 
or explicitly infer them.
We present a simple formalism that defines an ARG in terms 
of specific genomes and their intervals of genetic inheritance,
and show how it generalises these classical treatments and 
encompasses the outputs of recent methods. We discuss 
nuances arising from this more general structure, and argue that it
forms an appropriate basis for a software standard in this rapidly 
growing field.
\end{abstract}

>>>>

\begin{abstract}
As a result of recombination, adjacent nucleotides can have
different paths of genetic inheritance and therefore
the genealogical trees for
a sample of DNA sequences vary along the genome.
The structure capturing the details of these intricately interwoven paths of
inheritance is referred to as an ancestral recombination graph (ARG).
% New developments have made it possible to infer ARGs at scale,
% enabling many new applications in population and statistical genetics.
% This rapid progress has led to a diversity of ARG definitions and representations.
Classical formalisms have focused on mapping 
coalescence and recombination events to the nodes in an ARG.
We show that this approach is out of step with modern developments,
which do not represent genetic inheritance in terms of these events 
or explicitly infer them.
We present a simple formalism that defines an ARG in terms 
of specific genomes and their intervals of genetic inheritance,
and show how it generalises these classical treatments and 
encompasses the outputs of recent methods. We discuss 
nuances arising from this more general structure, and argue that it
forms an appropriate basis for a software standard in this rapidly 
growing field.
\end{abstract}
